### 2017-06-09 sheets/talk-6/sheet-6.tex
Sample solution 6.6

>>>>

\begin{answer}
  \begin{proof}
    We numerate the statements:
    \begin{itemize}
      \item  [I:]$s=t$
      \item [II:]The qualizer of $s$ and $t$ exists and is an isomorphism.
      \item[III:]The coequalizer of $s$ and $t$ exists and is an isomorphism.
    \end{itemize}
    We show that all statements are equivalent by showing $I \Leftrightarrow II$ and $I \Leftrightarrow III$.
    Note that $I \Leftrightarrow III$ is the dualized result of $I \Leftrightarrow II$, so we only need to show $I \Leftrightarrow II$.

    \begin{itemize}
      \item[``$\Rightarrow$'']
        Let $s=t$. Then the fork
        $\xymatrix{
          X \ar[r]^{1_X} & X \ar@<.5ex>[r]^s \ar@<-.5ex>[r]_t & Y
        }$
        $1_X$ is an isomorphism.
        Let
        $\xymatrix{
          A \ar[r]^f & X \ar@<.5ex>[r]^s \ar@<-.5ex>[r]_t & Y
        }$
        be a fork.
        Clearly $\bar{f} := f$ is the only map $\bar{f} \from A \to X$ such that the diagram
        \[ \xymatrix{
          A \ar[rd]^f \ar@{.>}[dd]|{\bar{f}} & & \\
          & X \ar@<.5ex>[r]^s \ar@<-.5ex>[r]_t & Y \\
          X \ar[ru]_{1_X} & &
        } \]
        commutes.
      \item[``$\Leftarrow$'']
        Let
        $\xymatrix{
          E \ar[r]^i & X \ar@<.5ex>[r]^s \ar@<-.5ex>[r]_t & Y
        }$
        be the equalizer and $i$ a isomorphism. Then by commutativity we get:
        \begin{alignat*}{4}
          && s \of i &= t \of i \\
          \Rightarrow  &\qquad& s \of i \of i^{-1} &= t \of i \of i^{-1} \\
          \Rightarrow  &      & s &= t
        \end{alignat*}\qedhere
    \end{itemize}
  \end{proof}
\end{answer}
